Computer Science House Constitution

### 2018-11-07 articles.tex
Clarifies Resignation
Check one:
[] Semantic Change: something about the meaning of the text is different
[x] Non-semantic Change: Spelling, grammar, or formatting changes.

Summary of change(s):
Probably a good idea to specify they are resigning a position they have.

\asection{Resignations}
An Executive Board Member may resign by submitting in writing the reason for resignation to the House Chairman.
The resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.

>>>>

\asection{Resignations}
An Executive Board Member may resign an Executive Board position currently held by submitting in writing the reason for resignation to the House Chairman.
The resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
